The Astropy Project

### 2017-10-31 main.tex
Update on Overleaf.
learn section

{\subsubsection{Circular Statistics}

@@

\subsection{Learning astropy}

>>>>

\subsubsection{Circular Statistics}

@@

\subsection{Learn Astropy}
% Adrian

The \astropypkg core package documentation contains narrative descriptions of
the package functionality along with detailed usage notes for functions,
classes, and modules.
While useful as a reference and for more advanced \python users, it is not the
right entry-point for all users or learning environments.
In the near future, we will launch a new resource for learning to use both the
\astropypkg core package and the many packages in the broader \astropy
ecosystem, under the name '\emph{Learn Astropy}.'

The new \emph{Learn Astropy} site will present several different ways to engage
with the \astropy ecosystem:
\begin{description}
    \item[Documentation] The \astropypkg and affiliated package documentation
        contain the complete description of a package with all requisite
        details, including usage, dependencies, and examples.
        The pages will largely remain as-is, but will be focused towards more
        intermediate users and as a reference resource.
    \item[Examples] These are stand-alone code snippets that live in the
        \astropypkg documentation that demonstrate a specific functionality
        within a subpackage.
        The \astropypkg core package documentation will then gain a new ``index
        of examples'' that links to all of the code or demonstrative examples
        within any documentation page.
    \item[Tutorials] The \astropy tutorials are step-by-step demonstrations of
        common tasks that incorporate several packages or subpackages.
        Tutorials are more extended and comprehensive than examples, may contain
        exercises for the users, and are generally geared towards workshops or
        teaching.
        Several tutorials already
        exist\footnote{\url{http://tutorials.astropy.org/}} and are being
        actively expanded.
    \item[Guides] These are long-form narrative, comprehensive,
        conceptually-focused documents (roughly one book chapter in length)
        providing stand-alone introductions to core packages in addition to the
        underlying astronomical concepts.
        These are less specific and more conceptual than tutorials.
        For example, ``using \astropypkg and \package{ccdproc} to reduce imaging
        data.''
\end{description}
We encourage any users who wish to see specific material to either contribute or
comment on these efforts via the \astropy mailing list or \astropy-tutorials
\github repository.\footnote{\url{https://github.com/astropy/astropy-tutorials}}
